---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- rmarkdown v1 -->

[![Build Status](https://travis-ci.org/gederajeg/scapr.svg?branch=master)](https://travis-ci.org/gederajeg/scapr) [![codecov](https://codecov.io/gh/gederajeg/scapr/branch/master/graph/badge.svg)](https://codecov.io/gh/gederajeg/scapr) [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# scapr

The goal of `scapr` is to turn lower-case character format into <span style = "font-variant:small-caps;">`small capitals`</span>. This function wrap the HTML-tag around a character string input as exemplified in Yihui Xie's chapter on inline-formatting for markdown syntax (cf.  [Bookdown](https://bookdown.org/yihui/bookdown/markdown-syntax.html)). I designed this function to help the writing of my thesis in R Markdown that deals with lots of small-capitalisation of words.

## Installation

You can install `scapr` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gederajeg/scapr")
```
## Example

```{r}
library(scapr)
```


We can use `scaps()` as an inline R code, e.g. to turn the word *happiness* into small caps, as follows: `` `r knitr::inline_expr('scaps("happiness")')` ``. It will then produce `r scaps("happiness")`.

There are three other functions in the package for different font-face types of the small-capital string. They are `scaps_italics()` (for `r scaps_italics("italicised small-captial string")`), `scaps_bold()` (for `r scaps_bold("boldfaced small-capital string")`) and `scaps_bolditalics()` (for both `r scaps_bolditalics("italicised and boldfaced small-capital string")`).
