---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active) [![Build Status](https://travis-ci.org/gederajeg/scapr.svg?branch=master)](https://travis-ci.org/gederajeg/scapr) [![Coverage status](https://codecov.io/gh/gederajeg/scapr/branch/master/graph/badge.svg)](https://codecov.io/github/gederajeg/scapr?branch=master)


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# scapr

The goal of `scapr` is to provide a set of functions that wrap over the HTML-tag for generating <span style = "font-variant:small-caps;">small capitals</span> strings. I designed this package to help me with the writing of my thesis in R Markdown that deals with lots of small-capitalisation of words to be rendered into MS Word output. The package aims to save time and, most importantly, prevent typo in writing the small capital tag (i.e., `<span style = "font-variant:small-caps;">a small capital string</span>`) over and over again in the R Markdown (cf. Yihui Xie's chapter in [Bookdown](https://bookdown.org/yihui/bookdown/markdown-syntax.html) about inline-formatting for small capital in R markdown). The `scapr` package can be seen as a complement to the [`lettercase`](https://cran.r-project.org/web/packages/lettercase/index.html) R package by Christopher Brown.

## Installation

You can install `scapr` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gederajeg/scapr")
```
## Example

```{r load-package, message = FALSE, warning = FALSE}
library(scapr)
library(dplyr)
```


The main function in the package is `scaps()`. It can be used as an inline R code in R Markdown as follows: `` `r knitr::inline_expr('scaps("happiness")')` ``. It will then turn "happiness" into "`r scaps("happiness")`". The alternative is to "pipe" `scaps()` after the target string: `` `r knitr::inline_expr('"happiness" %>% scaps()')` ``, which generates `r "happiness" %>% scaps()`. `scaps()` can also be used to modify strings in a data frame to be printed as table with `knitr` package:

```{r scaps-in-table}
# create the tibble/data_frame
df <- dplyr::tibble(concept = scaps(c("time", "emotion")),
                    freq = c(45, 53))

# print with knitr
knitr::kable(df, caption = "A table with small-capitalised strings")
```

There are three other functions in the package for different font-face types of the small capital string. They are `scaps_italics()` (for `r scaps_italics("italicised small captial string")`), `scaps_bold()` (for `r scaps_bold("boldfaced small capital string")`) and `scaps_bolditalics()` (for both `r scaps_bolditalics("italicised and boldfaced small capital string")`).

## Session info
```{r}
devtools::session_info()
rmarkdown::pandoc_version()
```

