---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
**Authors:** [Gede Primahadi Wijaya Rajeg](https://figshare.com/authors/Gede_Primahadi_Wijaya_Rajeg/1234749)<br/>
**License:** [GPL-2](https://www.gnu.org/licenses/old-licenses/gpl-2.0.en.html)<br/>

[![Travis-CI Build Status](https://travis-ci.org/gederajeg/scapr.svg?branch=master)](https://travis-ci.org/gederajeg/scapr)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# scapr

This package consists of one function (i.e., `scaps()`) for turning lower-case character format into <span style = "font-variant:small-caps;">`small capitals`</span>. This function wrap the HTML-tag around a character string input as exemplified in Yihui Xie's chapter on inline-formatting for markdown syntax (cf.  [Bookdown](https://bookdown.org/yihui/bookdown/markdown-syntax.html)). I designed this function to help the writing of my thesis that deals with lots of small-capitalisation of words.

The development version of the package can be installed via GitHub with [devtools](https://github.com/hadley/devtools):

```{r eval = FALSE}
library(devtools)
install_github("gederajeg/scapr")
```

## Example

```{r}
library(scapr)
```


We can use `scaps()` as an inline R code, e.g. to turn the word *happiness* into small caps, as follows: `` `r '\x60r scapr::scaps("happiness")\x60'` ``. It will then produce `r scaps("happiness")`.

Another example is to include another markdown formatting, such as **boldface** (e.g., `` `r '\x60r scapr::scaps("**happiness**")\x60'` `` that results in `r scaps("**happiness**")` and *italics* (e.g., `` `r '\x60r scapr::scaps("*happiness*")\x60'` `` that results in `r scaps("*happiness*")`.
